Energy Regulation for Biologically-Inspired Robotics

### 2021-09-20 latex/nserc/contributions.tex
Final version of contributions.

\item \textbf{Head Programming Mentor, FRC Team 2809, 2013 -- 2015}. 
    In this role, I mentored high school students in Object Oriented programming
    for robotics software. I taught students to program a robot in under 6
    weeks, which earned us 3rd place at the Ontario provincial competition in
    2014.
    In this role I learned to lead my students by giving them agency over the
    project, and to communicate with people from all over the world in
    high-stress situations.

>>>>

\item \textbf{Head Programming Mentor, FRC Team 2809, 2013 -- 2015}. 
    In this role, I mentored high school students in Object Oriented programming
    for robotics software. I taught students to program a robot in under 6
    weeks, which earned us 3rd place at the Ontario provincial competition in
    2014.
    In this role I became a better leader by listening to my students' feedback,
    and I learned to communicate effectively with people from all over the world
    in high-stress situations.
